---
title: "RStudio Connect Usage - Last 30 Days"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: styles.css
---
```{r preflight_check, results='asis', include=TRUE}
if (
  nchar(Sys.getenv("RSTUDIO_CONNECT_SERVER")) == 0 ||
  nchar(Sys.getenv("RSTUDIO_CONNECT_API_KEY")) == 0
) {
  print(htmltools::h4("ERROR: Variables Not Defined"))
  print(htmltools::div(
    "The RSTUDIO_CONNECT_SERVER and RSTUDIO_CONNECT_API_KEY",
    "environment variables are required in order for this report",
    "to pull usage data.",
    htmltools::br(),
    htmltools::br(),
    "Please define these variables",
    "and then re-run the report.",
    htmltools::br(),
    htmltools::br(),
    style = "max-width: 600px"
  ))
  knitr::knit_exit("Terminating the report early.")
}
```

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(DT)
library(plotly)
library(ggplot2)
library(shiny)
library(lubridate)
library(blastula)
library(prettyunits)

source("helpers.R")
source("themes.R")
shiny <- get_shiny_usage() %>% 
    clean_data()
content <- get_content_usage()
data <-   list(shiny = shiny, content = content)

```


This content summary may contain privileged information. The report is generated using the [RStudio Connect Server API](http://docs.rstudio.com/connect/api) and the source code is [available online](https://github.com/sol-eng/rsc-usage) if you'd like to customize your analysis. Data is limited to the last 30 days.

The report uses the environment variables `RSTUDIO_CONNECT_SERVER` and `RSTUDIO_CONNECT_API_KEY` to collect the data. To limit the results to a single publisher, use a publisher API key.

Column 
-----------------------------------------------------------------------

### Shiny Sessions by User (Top 5)

```{r}
data$shiny %>%
    group_by(user_guid) %>% 
    summarise(visits = n()) %>% 
    mutate(username = join_users(user_guid),
           username = null_chars(username, "anonymous")) %>% 
    select(username, visits) %>% 
    arrange(desc(visits)) %>% 
    head(5) %>% 
    {ggplot(., aes(reorder(username, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_rstudio() + 
     labs(
       y = "Number of Shiny Sessions",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```

### Content Hits by User (Top 5)

```{r}
data$content %>%
    group_by(user_guid) %>% 
    summarise(visits = n()) %>% 
    mutate(username = join_users(user_guid),
           username = null_chars(username, "anonymous")) %>% 
    select(username, visits) %>% 
    arrange(desc(visits)) %>% 
    head(5) %>% 
    {ggplot(., aes(reorder(username, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_rstudio() +
     labs(
       y = "Number of Content Visits",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```



Column 
-----------------------------------------------------------------------

### Shiny Sessions Over Time

```{r}
data$shiny %>%
    mutate(day = round_date(started, "day")) %>% 
    group_by(day) %>% 
    filter(day > today() - ddays(30)) %>% 
    summarise(visits = n()) %>% 
    arrange(desc(visits)) %>% 
    {ggplot(., aes(day, visits)) + 
     geom_point() +
     geom_smooth(se = FALSE) +
     theme_rstudio() + 
     labs(
       y = "# of Shiny Sessions",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```


### Content Visits Over Time

```{r}
data$content %>%
    mutate(time = ymd_hms(time),
          day = round_date(time, "day")) %>% 
    group_by(day) %>% 
    filter(day > today() - ddays(30)) %>% 
    summarise(visits = n()) %>% 
    arrange(desc(visits)) %>% 
    {ggplot(., aes(day, visits)) + 
     geom_point() +
     geom_smooth(se = FALSE) +
     theme_rstudio() + 
     labs(
       y = "Content Hits",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```

Column 
-----------------------------------------------------------------------

### Top Applications

```{r}
data$shiny %>% 
  group_by(content_guid) %>% 
  summarize(visits = n()) %>% 
  arrange(desc(visits)) %>% 
  head() %>% 
  mutate(name = sapply(content_guid, get_content_name)) %>% 
  {ggplot(., aes(reorder(name, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_rstudio() + 
     labs(
       y = "# of Shiny Sessions",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```

### Top Reports 

```{r}
data$content %>% 
  group_by(content_guid) %>% 
  summarize(visits = n()) %>% 
  arrange(desc(visits)) %>% 
  head() %>% 
  mutate(name = sapply(content_guid, get_content_name)) %>% 
  {ggplot(., aes(reorder(name, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_rstudio() + 
     labs(
       y = "Content Hits",
       x = NULL
     )} %>% 
    ggplotly(tooltip = c("y")) %>% 
    config(displayModeBar = F)
```


```{r}
content_summary <- data$content %>% 
  group_by(content_guid) %>% 
  summarize(visits = n()) %>% 
  arrange(desc(visits)) %>% 
  head() %>% 
  mutate(name = sapply(content_guid, get_content_name))

app_summary <- data$shiny %>% 
  group_by(content_guid) %>% 
  summarize(visits = n()) %>% 
  arrange(desc(visits)) %>% 
  head() %>% 
  mutate(name = sapply(content_guid, get_content_name))

leaderboard <- 
  rbind(app_summary, content_summary) %>% 
  ggplot(., aes(reorder(name, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     theme_rstudio() + 
     labs(
       y = "Visits",
       x = NULL
     )

body <- compose_email(
  body = "
  Hi Data Science Team!
  
  Here is the top viewed content for the last 30 days:
  
  {add_ggplot(leaderboard, width = 6, height = 6)}
  
  Best,
  
  RStudio Connect
  "
)
rmarkdown::output_metadata$set(
  rsc_email_subject = sprintf(" Content Usage Report For %s", month(today(), label = TRUE, abbr = FALSE)),
  rsc_email_body_html = body$html_str,
  rsc_email_images = body$images
)
```
