---
title: "bundle-diagnostics"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(purrr)
library(connectapi)
client <- connect()
```

## Enumerate Content List

```{r}
all_content <- get_content(client)

unpublished_content <- all_content %>% filter(is.na(bundle_id))
```


## Get Bundles for a Piece of Content

Beware:
- This only works for content you are a "collaborator" on. In this example, we
  only retrieve size data about the author's content (because it is easier to
  filter on). `get_user_permission()` and `get_group_permission()` can be used to
  figure out what content you are a collaborator on.
- As an administrator, another approach is to "add yourself to content,"
  "retrieve bundle data", then "remove yourself again". This will allow you to
  retrieve all bundle data, but will take longer and will add many audit log
  entries.
- Further, it is worth noting that this takes _a while_, because you have to iterate
  through each piece of content directly.
- We will explore improvements to the Connect access model in the future to make such
  reporting easier.

```{r}
my_guid <- client$me()$guid

my_content <- all_content %>% filter(purrr::map_lgl(owner, ~ .[["guid"]] == my_guid))
item_guid <- my_content[1,"guid"][[1]]


get_bundles_size <- function(client, guid) {
  message(glue::glue("Getting bundles for {guid}"))
  bundles_metadata <- get_bundles(content_item(client, guid))
  return(bundles_metadata[["size"]])
}

my_content_bundles_size <- my_content %>% 
  select(guid, name, title, description) %>%
  mutate(bundles = map(guid, ~ get_bundles_size(client, .x)))

my_bundles_tall <- my_content_bundles_size %>% 
  select(guid, bundles) %>% 
  tidyr::unnest(bundles) %>% 
  group_by(guid) %>% 
  mutate(row=row_number())

my_bundles_sum <- my_bundles_tall %>%
  group_by(guid) %>%
  summarize(total_size = sum(bundles), n = n())

```

## Summary of Sizes

```{r}
my_bundles_sum %>%
  summarize(
    n_content = n(), n_bundles = sum(n), total_size = sum(total_size),
    avg_size_per_content = total_size / n_content, avg_size_per_bundle = total_size / n_bundles
    )
```

## Top Content

```{r}
my_bundles_sum %>%
  arrange(desc(total_size)) %>%
  head(10)
```
