---
title: "User Usage"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

This document illustrates how to fetch user-level usage on your RStudio Connect server. This information can be useful for understand who is accessing Connect how many times, and for how long (for shiny apps). Note that this document will only return information that you are privy to. It is recommended for a user with admin privileges do this for the most complete data. 

This document will walk you though:

1. Getting your users.
2. Getting usage statistics for all non-shiny content by user. This provides visit totals.
3. Getting usage statitistics for shiny applications by user. This provides durations or visit totals.

## Environment Configuration

To ensure that your R session can communicate with the Connect API you must have the `CONNECT_API_KEY` and `CONNECT_SERVER` environment variables set. The recommended way to do this is with a `.Renviron` file. Alternatively you can use code like the below.

```{r}
## ACTION REQUIRED: Change the server URL below to your server's URL
Sys.setenv("CONNECT_SERVER"  = "https://connect.example.com/rsc") 

## ACTION REQUIRED: Make sure to have your API key ready
Sys.setenv("CONNECT_API_KEY" = "your-api-key-here")) 
```

## Example
 
Load requisite libraries and Connect to the API. 

```{r}
library(connectapi)
library(tidyverse)

client <- connect()
```

Fetch all of your users

```{r}
users <- get_users(client, page_size = Inf)
```

### Fetch Usage

In order to get complete usage statistics we need to get usage for Shiny apps and non-shiny apps. First we will grab usage statistics for all content from the past 200 days with `get_usage_static()`. For the purposes of a license renewal it is suggested to use your `from` date as the license start date. Following we will grab usage stats for shiny applications as well. 

```{r}
total_usage <- get_usage_static(client,
                                limit = Inf, 
                                from = Sys.Date() - 200,
                                to = Sys.Date())


shiny_use <- get_usage_shiny(client,
                limit = Inf, 
                from = Sys.Date() - 200,
                to = Sys.Date())

```

### Summarize Usage

For static content visits we can only know how many times a piece of content was visited. As such we will count the number of visits by each user. For shiny applications we can calculate the amount of time spent on a shiny application as well as the number of visits.

```{r}
# count non-shiny visits
count(total_usage, user_guid, sort = TRUE) %>% 
# join to shiny visits 
  left_join(
    shiny_use %>% 
      group_by(user_guid) %>% 
      summarise(shiny_usage = sum(ended-started),
                n_shiny_visits = n()) 
  ) %>% 
  rename(content_visits = n) %>% 
  # join to users for user identification
  left_join(select(users, first_name, last_name, user_guid = guid), 
            by = "user_guid") %>% 
  select(-user_guid)
```


