---
title: "RStudio Connect data"
author: "David Granjon"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme:
      version: 4
runtime: shiny
---

[Sourced from RinteRface/connectViz](https://github.com/RinteRface/connectViz)

```{r setup, include=FALSE}
#remotes::install_github("RinteRface/connectViz")
library(connectapi) # Tested with 0.1.0.9031
library(connectViz)
library(dplyr)
rsc_client <- create_rsc_client()
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)

days_back <- as.numeric(Sys.getenv("DAYSBACK", 90))
cache_location <- Sys.getenv("MEMOISE_CACHE_LOCATION", tempdir())
report_from <- lubridate::today() - lubridate::ddays(days_back)

```

```{r database}
# Get raw data from RSC database
get_apps_usage <- memoise::memoise(
  get_usage_shiny, 
  cache = memoise::cache_filesystem(cache_location)
  )
apps_usage <- get_apps_usage(rsc_client, from = report_from, limit = Inf)
rsc_content <- rsc_client %>% get_content()
rsc_users <- rsc_client %>% get_users(limit = Inf)
publishers <- rsc_users %>% filter(user_role == "publisher") 
shiny_apps <- rsc_content %>% filter(app_mode == "shiny")
# TO DO
# rsc_static <- rsc_client %>% get_usage_static(limit = Inf)
```

### General metrics

```{r general-metric, message=FALSE}
general_metrics <- list(
  "Onboarded Users (n)" = nrow(rsc_users),
  "Publishers (n)" = nrow(publishers),
  "Deployments (n)" = nrow(rsc_content),
  "Shiny Apps (n)" = nrow(shiny_apps)
)
shiny::fluidRow(
  align = "center",
  purrr::map(
    seq_along(general_metrics),
    function(i) {
      
      shinydashboard::infoBox(
        value = general_metrics[[i]],
        title = names(general_metrics)[[i]]
      )
    }
  )
)
```

### Shiny Apps usage

#### Most used apps

```{r}
apps_ranking <- create_app_ranking(rsc_content, rsc_users, apps_usage)
create_app_ranking_table(apps_ranking)
```

#### Daily app usage

```{r}
selectInput("selected_app", "Select an application", apps_ranking[[2]]$app_name)
daily_app_usage <- get_app_daily_usage(apps_ranking[[2]], reactive(input$selected_app))
create_app_daily_usage_chart(daily_app_usage)
```

#### Cumulated duration / user

```{r duration-plot}
create_cumulated_duration_per_user(apps_ranking[[1]], reactive(input$selected_app))
```

#### Number Hits / user

```{r sessions-plot}
create_cumulated_hits_per_user(apps_ranking[[1]], reactive(input$selected_app))
```

### Consumer data


#### Consumer ranking
```{r consumer-session-ranking}
numericInput(
  "views_threshold",
  "N view threshold",
  100,
  min = 0
)
consumer_ranking <- create_apps_consumer_ranking(apps_usage, rsc_users, reactive(input$views_threshold))
create_apps_consumer_ranking_chart(consumer_ranking)
```

#### Daily app consumption

```{r daily-app-consumption-per-user}
selectInput("selected_user", "Select an application", rsc_users$username)
daily_consumption <- get_user_daily_consumption(rsc_content, rsc_users, apps_usage, reactive(input$selected_user))
create_user_daily_consumption_chart(daily_consumption)
```


### Developers data


#### Developers ranking (number of deployments: api, static, shiny, rmd, ...)

```{r developers-ranking}
developers_apps_ranking <- create_dev_ranking(rsc_users, rsc_content)
numericInput(
  "apps_threshold",
  "N app threshold",
  5,
  min = 1,
  max = developers_apps_ranking %>% pull(n_apps) %>% max()
)
create_dev_ranking_chart(developers_apps_ranking, reactive(input$apps_threshold))
```

#### Developer projects overview

```{r}
selectInput(
  "app_developer",
  "Select a developer",
  developers_apps_ranking$username
)
create_dev_project_overview(developers_apps_ranking, rsc_client, apps_ranking[[1]], reactive(input$app_developer))
```


### Other data

#### Users repartition (%)

```{r user-repartition}
# I realized some users are not active (ie active_time is NA).
# Maybe to remove from the viz in the future?
sort_users_by_role(rsc_users) %>% create_pie_chart("user_role")
```

#### Content access

How do people protect their content?

```{r content-access-type}
sort_content_by_access(rsc_content) %>% create_pie_chart("access_type")
```


#### R versions

What are the R versions used?

```{r content-r-version}
sort_content_by_rversion(rsc_content) %>% create_pie_chart("r_version")
```

#### Content type

```{r content-type}
sort_content_by_appmode(rsc_content) %>% create_pie_chart("app_mode")
```
