---
title: "App Visitation"
date: "`r Sys.Date()`"
params:
  from: !r Sys.Date() - 10
  to: !r Sys.Date()
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

## Objective

The objective of this report is to be able to quickly identify the usage of all shiny applications used within a specified date range. This is a complement to the existing [Connect Usage Dashboard](https://github.com/sol-eng/connect-usage/tree/master/examples/last_30_days). The Connect Usage Dashboard provides high level statistics about the usage of shiny apps across the server. Whereas this report tells us about each individual app. 


## Generating the Report

In this code chunk we connect to an existing pin that contains the enumeration of all pieces of content on the server. Since fetching this information can be rather slow depending on the amount of content on the server, it was collected and stored in a pin ahead of time. By doing so, we increase the speed of the parameterized report. See `server-content-list.R`. 


```{r content-list, message=FALSE, warning=FALSE}
library(connectapi)
library(reactable)
library(dplyr)

# connect to the pin board
pins::board_register_rsconnect(server = Sys.getenv("CONNECT_SERVER"),
                               key = Sys.getenv("CONNECT_API_KEY"))


# get all content listings from pin (this is slow so store it in a pin)
all_content <- pins::pin_get("josiah/rsc_content_list", board = "rsconnect")
```

Here we connect to the RStudio Connect (RSC) API using the `connectapi` package. We then fetch usage statistics for Shiny apps within the range specified by the input parameters stored in the objects `params`. 

```{r pressure, echo=FALSE}
# connect to RSC and make R6 object
client <- connect()

# fetch all shiny use data from specified time period
shiny_use <- get_usage_shiny(client,
                             limit = Inf, 
                             from = params$from,
                             to = params$to)
```

The below chunk calculates visit duration, joins to the content listing (`all_content` object), and then summarizes the visitation for each app. 

```{r, message = FALSE, warning=FALSE}
# select only desired shiny data
shiny <- shiny_use %>% 
  mutate(duration = ended - started) %>%
  select(content_guid, user_guid, duration)


cleaned_metrics <- all_content %>% 
  select(guid, title, url, owner_username) %>% 
  inner_join(shiny, by = c("guid" = "content_guid")) %>% 
  # summarise statistics
  group_by(guid, owner_username, url, title) %>%
  summarise(duration_mins = round(as.numeric(sum(duration), units = "mins"), 2),
            max_duration = round(as.numeric(max(duration), units = "mins"), 2),
            n_visits = n(),
            data = list(as.numeric(duration))) %>%
  ungroup() %>%
  select(-guid) %>%
  arrange(-duration_mins) 

```

```{r, echo= FALSE}
reactable(
  cleaned_metrics,
  filterable = TRUE,
  sortable = TRUE,
  columns = list(
    title = colDef(
      html = TRUE,
      cell = function(value, index) {
        glue::glue("<a href={cleaned_metrics[index,'url']}>
                     {value}</a>")
      }),
    url = colDef(show = FALSE),
    data = colDef(cell = function(values) {
      
    #if (!is.numeric(values)) return()
    sparkline::sparkline(as.numeric(values), type = "line", width = 100, height = 30)
  },
  name = "")
    )
)
```



